---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r load_data}
install.packages("plyr", repos = "http://had.co.nz/plyr")
library(plyr)
install.packages("ggplot2", repos = "https://github.com/hadley/ggplot2")
library(ggplot2)

unzip("activity.zip")
data <- read.csv("activity.csv", header = T)
summary(data)
```


## What is mean total number of steps taken per day?
For this part of the assignment, you can ignore the missing values in the dataset.

1. Calculate the total number of steps taken per day
```{r daily_aggregate}
dailySteps <- ddply(data, ~date, summarize, steps=sum(steps, na.rm=T))
```

2. If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day
```{r daily_hist}
hist(dailySteps$steps, breaks = seq(0,25000,by=1000), 
     main = "Frequency of Daily Steps", xlab = "Daily Steps", col = "grey")
```

3. Calculate and report the mean and median of the total number of steps taken per day
```{r med_mean}
median(dailySteps$steps, na.rm=T)
mean(dailySteps$steps, na.rm=T)
```

## What is the average daily activity pattern?
1. Make a time series plot (i.e. ðšðš¢ðš™ðšŽ = "ðš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
intervalSteps <- ddply(data, ~interval, summarize, steps=mean(steps, na.rm=T))
i <- qplot(interval, steps, data=intervalSteps)
i + geom_line() + geom_point(mapping=NULL)
```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
intervalSteps[which(intervalSteps$steps == with(intervalSteps, max(steps))), "interval"]
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
